---
title: "VE572 Assignment 3"
author: "Liu Yihao 515370910207"
date: "2018-6-26"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Qurestion 1

### (a)
$$Pr(Y=1|X_1=x_1|X_2=x_2)=\frac{\exp(\beta_0+\beta_1x_1+\beta_2x_2)}{1+\exp(\beta_0+\beta_1x_1+\beta_2x_2)}$$
$$Pr(Y=1|X_1=40|X_2=3.5)=\frac{\exp(-6+0.05\cdot40+3.5)}{1+\exp(-6+0.05\cdot40+3.5)}\approx0.378$$

### (b)
$$\frac{\exp(-6+0.05x_1+3.5)}{1+\exp(-6+0.05x_1+3.5)}=0.5$$
$$\exp(-6+0.05x_1+3.5)=1$$
$$x_1=50$$

## Question 2

### (a)
$$odds(U.S.A|Y=1)=\frac{513}{487}$$
$$odds(China|Y=1)=\frac{116}{9}$$

### (b)
$$OR=\frac{513/487}{928/72}=\frac{4617}{56492}\approx8.173\times10^{-2}$$

### (c)
$$\beta_0=\ln\frac{116}{9}\approx2.5819$$
$$\beta_0+\beta_1=\ln\frac{513}{487}$$
$$\beta_1=\ln\frac{4617}{56492}\approx-2.5043$$

### (d)
$$\beta_1=\ln(OR)$$

### (e)
$$\exp[\ln(OR)\pm1.96\times SE(\ln(OR))]=[0.0624,0.1071]$$

## Question 3

### (a)
$$\int_0^{0.05}0.05+xdx+\int_{0.05}^{0.95}0.1dx+\int_{0.95}^10.1-xdx=9.75\%$$

### (b)
$$9.75\%\times9.75\%=0.950625\%$$

### (c)
$$\sqrt[100]{0.1}$$

## Question 4

### (a)
```{r ex4, fig.height=4, fig.width=4, fig.align='center', echo = F}
plot(0:10, 0:10, type = 'n', xlab = 'X1', ylab = 'X2')
x0 = c(2, 4, 4, 6)
y0 = c(4, 2, 6, 4)
x1 = c(4, 6)
y1 = c(4, 2)
points(x0, y0, col = 'red', pch = 4)
points(x1, y1, col = 'blue', pch = 3)
rect(3, 3, 5, 5)
rect(5, -1, 11, 3)
legend("topright", c("Y=0","Y=1"), col = c('red', 'blue'), pch = c(4, 3))
```

### (b)
$$Y(8,1)=1$$

## Question 5

### (a)
First, $C_1=(-1.5,0)$, $C_2=(1.5,0)$, so $(-2,0.5)$ should be assigned to $C_2$ and $(2,-0.5)$ should be assigned to $C_1$.

Second, $C_1=(-2.5,0)$, $C_2=(2.5,0)$, so converges.

### (b)
First, $C_1=(0,0)$, $C_2=(0,0)$, we can find that all points have the same distance to the two centersm so converges.

I notice that different initialization can give very different results in K-means clustering, so the randomness of initialization is very important.


## Question 6

### (a)
```{r q6.a, echo=FALSE}
m = matrix(c(0,0.3,0.4,0.7, 0.3,0,0.5,0.8, 0.4,0.5,0,0.45, 0.7,0.8,0.45,0), nrow = 4, ncol = 4)
hc = hclust(as.dist(m), method = "complete")
plot(hc)
ct = cutree(hc, k = 2)
```

### (b)
```{r q6.b, echo=FALSE}
m = matrix(c(0,0.3,0.4,0.7, 0.3,0,0.5,0.8, 0.4,0.5,0,0.45, 0.7,0.8,0.45,0), nrow = 4, ncol = 4)
hc = hclust(as.dist(m), method = "single")
plot(hc)
ct = cutree(hc, k = 2)
```

### (c)
Observations 1, 2 in $C_1$ and 3, 4 in $C_2$

### (d)
Observations 1, 2, 3 in $C_1$ and 4 in $C_2$






